### 2024-10-07 esop25/cpj.tex
checkpoint

Our main type safety result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\cnote{Need to define gradual release... should probably have a section
  where we summarize hyperproperties.}
\begin{theorem}
  If $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is valid and there exists no $H,C$ 
  and  $\sx{w}{\cid}$ for $\cid \in H$ with $\leakj{\Gamma}{C}{\setit{\sx{w}{\cid}}}$,
  then $\prog$ satisfies gradual release.
\end{theorem}

>>>>

\subsubsection{Type Safety}

\cnote{Define (conditional) inputs in hyperproperties section.}

\begin{definition}
  \label{definition-sound}
  Given $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  and $\flips(\prog) = R$, we say that
  \emph{$\Gamma$ is sound for $\prog$} iff for all $M' \subseteq M$
      and $X \subseteq S \cup R$, the following
      conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
    \item  if $X$ are inputs to $M'$ then
      there exists $\ty$ with $\leakj{\Gamma}{M'}{\ty}$ and $X \subseteq \ty$.
    \item  for all  $R' \subseteq R$, if
      $X$ are $R'$ are conditional inputs to $M'$ then $\leakj{\Gamma}{M'}{\ty}$
      and $\leakclose{\Gamma}{\ty \cup R'}{\ty'}$ and $X \subseteq \ty'$.
  \end{enumerate}
\end{definition}

\begin{lemma}
  \label{lemma-cpjsound}
  If $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is valid then $\Gamma$ is
  sound for $\prog$.
\end{lemma}
\begin{proof}
  Unrolling Definition \ref{definition-sound}, proceed by induction on $M'$.
  In case $M' = \varnothing$ the result follows trivially. Otherwise XXX
\end{proof}

Our main type safety result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\cnote{Need to define gradual release... should probably have a section
  where we summarize hyperproperties.}
\begin{theorem}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and there exists no $H,C$ such that $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T \ne \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemma \ref{lemma-cpjsound} and definition of gradual release.
\end{proof}
